Data Exploration

### 2019-02-21 src/data_exploration.Rmd
loop creation - could do with unique year and unique month something... but stack name..

```{r}
library(dismo)
library(rJava)
jar <- paste(system.file(package="dismo"), "C:/Users/bunny/Documents/GitHub/Chapter_1/packrat/lib/x86_64-w64-mingw32/3.5.1/dismo/java/maxent.jar", sep='')
p
testmax <- maxent(janpresmax, janabmax)
```

>>>>

zt stratified stack with layer names that match swd
```{r}
ascname <- list.files("../data/jan_test_86.9", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks
noasc <- length(ascname)
  year <- "1998"
  month <- "01"
  depth <- "86.9294.asc"
  tempvar <- "temp"
  chlvar <- "chl"
  o2var <- "o2"
  salvar <- "salinity"
  depthvar <- "depth"
  surfacevar <- "surface"
  naovar <- "nao"
  amovar <- "amo"
  samplevar <- "sample"
  wintervar <- "winter"

for (i in 1:length(asclist)){
  ascyear <- (sapply(strsplit(ascname[i], "_"), "[[", 1))
  ascmonth <- (sapply(strsplit(ascname[i], "_"), "[[", 2))
  ascdepth <- (sapply(strsplit(ascname[i], "_"), "[[", 5))
  ascvar1 <- (sapply(strsplit(ascname[i], "_"), "[[", 3))
  ascvar2 <- (sapply(strsplit(ascname[i], "_"), "[[", 4))
  ascfile <- ascname[i]

  if (ascyear == year & ascmonth == month & ascvar1 == tempvar & ascvar2 == depthvar & ascdepth == depth){
    #print(ascfile)
    temp_depth <- raster(ascfile)
    names(temp_depth) <- "temp_depth"
  } else if (ascyear == year & ascmonth == month & ascvar1 == chlvar & ascvar2 == surfacevar & ascdepth == depth){
    chl_surface <- raster(ascfile)
    names(chl_surface) <- "chl_surface"
  } else if (ascyear == year & ascmonth == month & ascvar1 == o2var & ascvar2 == depthvar & ascdepth == depth){
    o2_depth <- raster(ascfile)
    names(o2_depth) <- "o2_depth"
  } else if (ascyear == year & ascmonth == month & ascvar1 == salvar & ascvar2 == depthvar & ascdepth == depth){
    salinity_depth <- raster(ascfile)
    names(salinity_depth) <- "salinity_depth"
  } else if (ascyear == year & ascmonth == month & ascvar1 == naovar & ascvar2 == samplevar){
    nao_sample <- raster(ascfile)
    names(nao_sample <- "nao_sample")
  } else if (ascyear == year & ascmonth == month & ascvar1 == naovar & ascvar2 == wintervar){
    nao_winter <- raster(ascfile)
    names(nao_winter) <- "nao_winter"
  }
  st19980186.9 <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)

}

chl_surface <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*chl_surface_86.9294*.asc"), full.names = TRUE))
names(chl_surface) <- "chl_surface"
nao_sample <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*nao_sample_86.9294*.asc"), full.names = TRUE))
names(nao_sample) <- "nao_sample"
nao_winter <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*nao_winter_86.9294*.asc"), full.names = TRUE))
names(nao_winter) <- "nao_winter"
o2_depth <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*o2_depth_86.9294*.asc"), full.names = TRUE)) 
names(o2_depth) <- "o2_depth"
salinity_depth <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*salinity_depth_86.9294*.asc"), full.names = TRUE))
names(salinity_depth) <- "salinity_depth"
temp_depth <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*temp_depth_86.9294*.asc"), full.names = TRUE))
names(temp_depth) <- "temp_depth"

stack1998_01_86.9294 <- stack(chl_surface, nao_sample, nao_winter, o2_depth, salinity_depth, temp_depth)

asclist <- (list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*_86.9294*.asc"), full.names = TRUE))    # this folder currently contains other dummy files. its just a test to automate stacks
ascfile <- names(asclist[[1]])
ascyear <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 1))
ascmonth <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 2))
ascdepth <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 5))
ascname <- paste(ascyear, ascmonth, ascdepth, sep = "_") #once you figure out how to rename the layers in the stack, you will rename the stack this () or not - maybe just manual
asclist # now need to rename to match maxent expectations

```{r}
library(dismo)
library(rJava)
jar <- paste(system.file(package="dismo"), "C:/Users/bunny/Documents/GitHub/Chapter_1/packrat/lib/x86_64-w64-mingw32/3.5.1/dismo/java/maxent.jar", sep='')
file.exists(jar)
testmax <- maxent(janpresabmax, janpresabmax$occurrence)
